
\section*{Human Subjects Protection}

Data associated with human subjects includes high speed videos, motion capture data, and other data
    modalities collected for everyday manipulation tasks.  As part of
  our study of manipulation, we will collect video and RGB-D data of
  our human subjects in natural settings, and motion capture data,
  force data, and other data modalities in our motion capture lab.




\subsection*{Potential Risks to Human Subjects}

The risks and discomfort associated with participation in these
studies will be no greater than those ordinarily encountered in daily
life or during the performance of routine physical or psychological
examinations or tests.  Should optical markers be used to measure
motion, subjects may experience a small amount of discomfort when the
optical markers are removed (equivalent to removing a bandaid from the
skin.)

\subsection*{Plans for Recruitment}


Subjects will be recruited throughout the CMU campus through posted
advertisements and an email mailing list.   Subjects of both genders
will be recruited equally.  The experiments will be restricted to
adult subjects who give voluntary consent to participate and who will
be instructed that they may terminate their participation in the study
at any time.   A small monetary compensation may be
provided for participation in the study.


\subsection*{Informed Consent}

Subjects will be given a written document outlining the goals of the
study, its duration, and the nature of the tasks they will be asked to
perform.  The consent document will have information on whom to
contact should they have any questions or concerns after the study,
and they will be given a copy of this document to take with them.

The confidentiality statement given to human subjects for our studies
is expected to be worded as follows:

``By participating in the study, you understand and agree that
Carnegie Mellon may be required to disclose your consent form, data
and other personally identifiable information as required by law,
regulation, subpoena or court order. Otherwise, your confidentiality
will be maintained in the following manner: 

Your data and consent form will be kept separate. Your consent form
will be stored in a locked location on Carnegie Mellon property and
will not be disclosed to third parties. By participating, you
understand and agree that the data and information gathered during
this study may be used by Carnegie Mellon and published and/or
disclosed by Carnegie Mellon to others outside of Carnegie
Mellon. However, your name, address, contact information and other
direct personal identifiers in your consent form will not be mentioned
in any such publication or dissemination of the research data and/or
results by Carnegie Mellon.

I understand that the following procedures will be used to maintain my
anonymity in analysis and publication/presentation of any results: (1)
Each participant will be assigned a number, names will not be
recorded. (2) The researchers will save the data file and/or any video
or audio recordings by participant number, not by name. The data and
video will be stored on the web and free access will be granted to
researchers and others. The videotape may be of sufficient quality for
someone to recognize me. I may request to see my data visualized and
may request that particular trials from a session be deleted if I
prefer that my performance not be included in the database. I may
request that the researchers remove the video clips from the web
database at any time in the future.''

\subsection*{Inclusion of Women, Minorities, and Children}

Women and minorities will be recruited equally among all other abled
adult members of the population.   Participants in the study will be
required to be 18 years of age or older.
