\section{Summary}

Introduction:

Dexterity is a Grand Challenge goal in robotics today, and is on the critical path to capable robots in almost every domain:  home, work, space, medicine, disaster scenarios...    With advances in rapid prototyping and design optimization, we are well poised for dramatic progress in robot dexterity.   Rapid prototyping technologies are becoming available in every lab.    New robot hands are being designed at an unprecedented pace.

However, we are missing one crucial ingredient:  we do not yet fully understand manipulation.   We have no clear guidelines for creating the robot dexterity that would cause a transformative advance.   The lack of clear design goals is a great barrier to further progress, and we as a field are struggling greatly to create reliable, apparently effortless dexterous behavior.

Our proposal aims to address this gap.   We have observed patterns in human manipulation strategies and actions such that we are able to create Grasp Nets representing families of dexterous behavior.    These Grasp Nets provide the design focus that has been lacking.    Our expertise in grasp and manipulation analysis (PI Pollard) and optimal design, rapid prototyping, and control (PI Coros) make us the perfect team to convert these observations  into robot hands that present previously unseen levels of robust dexterous behavior.

Intellectual Merit:

Our working principles and research questions are that:
(A) On-task compliance reduces actuator requirements.   This is important for dexterous manipulation, because keeping number of actuators low and size of actuators small makes it possible to design lightweight hands with less tendon routing (or other actuator complexity to get them off board of the hand).
(B) Joint limits improve robustness to error and likely make it easier to learn a task.
(C) Working from specific Grasp Nets (such as we observe people to use) focuses design efforts and will make possible the next quantum leap in design for dexterous manipulation.

We will advance the state of the art in:
(1) Creation of Grasp Nets capturing broadening collections of grasping and manipulation capability as observed in human performance.
(2) Design, modeling, and optimization of compliant elements to simplify manipulation task performance.
(3) Analysis of manipulation with joint limits.
(4) Design and optimization of joint limit surfaces to improve robustness of grasping and manipulation actions.
(5) Development of models of error and variation in state of the art manufacturing technologies as they relate to dexterous manipulation.
Together, these contributions will make possible for the first time reliable and broadly varying dexterous behavior from accessible designed prototyping technologies.

Broader Impact:

Having truly dexterous robots will affect many areas of our lives.   If robots can suddenly use their hands in a dexterous manner, they will be able to create nontrivial effects on the world and be capable of rendering competent assistance in manual tasks and applications can improve our quality of life, our health, and our safety.     Educational broader impact includes K-12 outreach efforts.  For example, we have recently brought the discussion of robot hands in to the elementary school classroom.    Evaluation metrics will be available to be part of the continuing efforts to develop grasping and manipulation benchmarks.   Grasp Nets and robot hand designs will be made available so that others can easily access and build upon our results.   The PIs have an excellent track record with mentoring underrepresented students and undergraduates and will continue this trend.


